ms_0_intro

### 2017-11-08 man/ms_0_intro.Rmd
add more ideas to intro

Ideas a expresar

### Remote sensing

@@

Although summer drought is a characteristic feature of the Mediterranean climate [@Lionello2012], an increase in the frequency and severity of drought events have been recorded for the Mediterranean region [@Hoerling2011], particularly for southern Europe [@VicenteSerrano2014; @Spinoni2015; @Stagge2017] where a trend towards drier summers has been reported for the last three decades [@Spinoni2017b].

### Ideas a incluir

* :red_circle: Algo de las sequías de 2005 y 2014

* Extreme sequías y ecología

frecuencia de las sequías severas (ver Dai 2011)

* Extreme sequias y ecologia 
* Como la dendro ayuda a evaluar las sequías (ver Gazol 2017)

Extreme climate events (as droughts, heatwaves) severely affect forests and grasslands throuhg changes in plant physiology, phenology and carbon allocation [@Ummenhofer2017].

Droughts are most likely to have the largest and most long-lasting impacts globally due to large indirect and lagged impacts and long recovery especially for forest ecosystems (ver  18 en @Ummenhofer2017)

>>>>

Although summer drought is a characteristic feature of the Mediterranean climate [@Lionello2012], an increase in the frequency and severity of drought events have been recorded for the Mediterranean region [@Hoerling2011], particularly for southern Europe [@VicenteSerrano2014; @Spinoni2015; @Stagge2017] where a trend towards drier summers has been reported for the last three decades [@Spinoni2017b]. Además las proyecciones apuntan a que este incremento en la frecuencia continuará [@Spinoni2017a].

### Extreme sequias y ecologia

Extreme climate events (e.g. droughts) severely affect forests and grasslands throuhg changes in plant physiology, phenology and carbon allocation [@Ummenhofer2017] (incluir citas para los efectos de la sequía sobre la vegetación).

No solo efectos aislados, sino también en conjunción con otros factores, sobre todo en el mediterráneo donde convergen muchos de los factores que pueden interaccionar:

* La sequía es un factor crucial a tener en cuenta, ya que es además de los efectos que puede tener de forma aislada, se ha visto que además presenta muchas interacciones con otros factores, siendo por tanto un factor crucial (`$IMPROVE$` ver [@DoblasMiranda2017]):
* Some interactions alter the effects of a single factor, as drought enhances or decreases the effects of atmospheric components on plant ecophysiology
* Drought and land use changes, among others, alter water resources and lead to land degradation, vegetation regeneration decline, and expansion of forest diseases.
* Climate change, and especially drought, emerges as a crucial factor in most of the reviewed interactions and therefore it should be considered when it comes to designing and applying international management policies
* Drought should be considered when designing and applying management policies.

Además la sequía se espera que tengan ...Droughts are most likely to have the largest and most long-lasting impacts globally due to large indirect and lagged impacts and long recovery especially for forest ecosystems (ver  18 en @Ummenhofer2017). Así por ejemplo se ha visto que todos los biomas presentan una vulnerabilidad similar ...
En una revision sobre la vulnerabilidad del sistema de trasnporte en plantas al embolismo inducido por sequía, ha mostrado que una convergencia de la vulnerabilidad de los bosques a la sequía, mostrando que todos los biomas son igualmente vulnerables a los fallos hidráulicos independientemente del régimen de precipitación (Choat et al. 2012, doi:10.1038/nature11688)

-- Existen evidencias que sugieren que muchos bosques son vulnerables a eventos climáticos extremos ... (Zhang) y esto puede ser especialmente relevante para especies situadas en el rear edge (completar)

Una vez dicho esto...

* Como la dendro ayuda a evaluar las sequías (ver Gazol 2017) 
* Remote sensing:

@@
